Asymptotic Validity of the Bayes-Inspired Indifference Zone Procedure: the Non-Normal Known Variance Case

### 2015-06-13 montreal/presentation.tex
modifications

\end{block}
\begin{itemize}
\item The mapping from $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where $Y_{tx}$ is the sum of the first $t$ samples from alternative
$x$, onto $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
where $Z_{tx}=Y_{n_{tx},t}$ is the sum of samples from alternative
$x$observed by stage $t$.\\
\textrm{}\\
\item The second maps the previous time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where
\[
q_{tx}^{'}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right)\right.
\]

>>>>

\end{block}
\begin{itemize}
\item The mapping from $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where $Y_{tx}$ is the sum of the first $t$ samples from alternative
$x$, onto $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
where $Z_{tx}=Y_{n_{tx},x}$ is the sum of samples from alternative
$x$ observed by stage $t$.\\
\textrm{}\\
\item The second maps the previous time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where
\[
q_{tx}^{'}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right)\right.
\]
